\chapter{Outline}\label{chapter:Outline}

The study of variations in the space environment between the Sun and the Earth constitutes 
the core of \textit{space weather} research. Ionised plasma ejected by the Sun couples with 
the Earth’s magnetic field in complex processes that determine the state of the Earth's 
magnetosphere. Adverse effects from space weather can impact communication networks, 
power grids, and logistics infrastructure, which are all crucial pillars of a civilization that 
is reliant on technology.

It is important to leverage data sources, scientific knowledge and machine learning 
techniques to create space weather forecasting and monitoring systems of the future. This 
thesis aims to be a step towards that goal. 

\section{Research Questions}

The research questions addressed in this dissertation center around three key themes.

\begin{enumerate}
    \item \textit{Standard Forecasting}: How can we create probabilistic forecasting systems 
    for key geomagnetic quantities? What is the time horizon for such forecasts? Is it possible 
    to get accurate predictions while increasing the forecast horizons?
    
    \item \textit{Parameter Inference \& Uncertainty Quantification}: Are machine learning models 
    and physics models two separate pieces or can they be a married together in a way which enables 
    identification of unobserved physical parameters?  
    
    \item \textit{Dynamic Time Lag Regression}: How can we predict near Earth solar wind speed 
    and its propagation time from solar data? More generally, is it possible to infer using time 
    series data \emph{when} the impacts of events will be felt at their downstream destinations? 
    This is different from standard forecasting which is always concerned with predictions made 
    with a \emph{fixed} time horizon.
\end{enumerate}
    
\section{Chapter Outline}

The dissertation is organised as follows.

\begin{itemize}
    \item \Cref{chapter:introduction} provides context for the space weather project and its 
    links to terrestrial weather via historical anecdotes. It highlights impacts of space weather 
    events and speculates why space weather research will become even more important in the coming 
    decades.

    \item \Cref{chapter:preliminaries} gives a short introduction to the concepts needed 
    to understand the problems considered in this thesis. \Cref{sec:mag} talks about the 
    magnetosphere and the motions of charged particles trapped within it. This is the starting 
    point for the material in \cref{chapter:dst_osa,chapter:dst_msa,chapter:bayes_diff_chapter}. 
    \Cref{sec:solar} gives a quick overview about the structure of the Sun, its magnetic field, 
    and the solar wind which is the target application of the method proposed in \cref{chapter:pdt}.
    
    \item \Cref{chapter:dst_osa} applies \emph{Gaussian process} (GP) models for making 
    probabilistic forecasts of Earth based geomagnetic quantities and gives a practical methodology 
    for building and evaluating such models. \Cref{chapter:dst_msa} extends the time horizon of the 
    forecasting models proposed in \cref{chapter:dst_osa} by proposing a hybrid model based on 
    \emph{long short-term memory} (LSTM) networks and Gaussian processes.
    
    \item \Cref{chapter:bayes_diff_chapter} proposes a model based on the 
    \emph{least squares support vector machine} (LSSVM) for estimating magnetospheric plasma 
    density. The parameters of the model are estimated by minimizing error with respect to observed 
    data and the physical dynamics of plasma diffusion. Combining this with 
    \emph{Markov chain Monte Carlo} methods, we obtain Bayesian estimates on unobserved 
    parameters of the plasma diffusion system.   
    
    \item \Cref{chapter:pdt} introduces \emph{dynamic time lag regression} (\XX) a novel 
    supervised regression framework which captures probabilistic and dynamic propagation time 
    delays between time series. We propose a solution methodology for the \XX \ setting and provide 
    a theoretical framework for understanding its convergence. The \XX \ methodology is applied to 
    the forecasting of solar wind speed from solar magnetic data. 
    
    \item \Cref{chapter:conclusions} discusses the progress made in the thesis and offers 
    perspectives for future research.
\end{itemize}


\Cref{chapter:dst_osa,chapter:dst_msa} are based on published journal articles 
while \cref{chapter:bayes_diff_chapter,chapter:pdt} are based on work that is in peer review or in 
preparation for publication.  