\chapter*{Acknowledgements}\label{chapter:preface}

Thank you Enrico for giving me this opportunity, for your guidance, and your 
belief in me. Mich\'el\`e and Ute, you have both taught me, in your own ways, 
what real leadership is about. Cyril, thank you for teaching me that patient 
rumination and deep thinking are still relevant in today's world. Bala, 
your wisdom and support elevated the quality of our research, you are 
the kind of scientist the community needs and I wish you the very best.

I would like to thank Peter Gr\"{u}nwald for his guidance, wisdom, and 
thoughtfulness during the manuscript preparation process. Peter, you are truly 
a beacon for young scientists. 

Behnaaz, we wont be able to continue our afternoon gossip sessions, but you 
should keep at it because gossip is known to lead to a long and happy life. 
Ashutosh, Casper, and Gabriel, your company meant that there was never a dull 
day at the office. Algo, always remember that the world is a non-linear, 
non-stationary, chaotic dynamic system at the edge of criticality, so if 
you have a sample of 100 clean data points and a sample of 100 corrupted data 
points, you should add noise to the clean data set, in order to equalise the 
disaster.

Rakesh and Carl(os), I will always remember and miss our hilarious chats, very 
nice! Hani, never change! Giancarlo, salud to Parisian evenings with Armagnac. 
Monsieur Philippe, continuez \`a faire ces sublimes galettes.
%
Nada and Bikkie, you make CWI a great place to work. I would not have gotten 
through this PhD so smoothly if it wasn't for you guys!  

Divya, without you, none of this would have ever happened!
%
Aai and Baba, I am what I am today because of the childhood that you provided 
me. An upbringing that was full of curiosity, support, travel, wisdom, and love.